\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-23 icse20/eval.tex
Slight updates in evaluation

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 1,601 algorithms in ECMAScript 2020,
\inred{XXX} algorithms are relevant to the excluded language features
discussed in Section~\ref{sec:exclusion}, and \inred{XXXX} algorithms
are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining \inred{XXX} algorithms, we selected \inred{XX}
algorithms that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions.

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of \inred{August 6, 2019}.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also excluded \inred{XXXX}
tests for excluded features and non-standard negative tests.
Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
interpreter and they all successfully passed, which means that all the
semantics extracted from \( \tool \) are perfectly correct.

>>>>

To evaluate the correctness of \( \tool \), we developed a JavaScript
interpreter based on the extracted syntax and semantics from
ECMAScript 2020.  Among 9,657 steps in ECMAScript 2020,
8,926 steps are automatically compiled via \textsf{Algorithm Compiler}.
Among the remaining 731 steps, we selected 381 steps
that are essential to the core semantics and manually
implemented their corresponding \( \ires \) functions
via the rule assistant introduced in Section~\ref{sec:assistant}.
Moreover, we implement the \textsf{Global Setting} except
the excluded language features discussed in Section~\ref{sec:exclusion}.

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also excluded \inred{XXXX}
tests for excluded features and non-standard negative tests.
Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
interpreter and they all successfully passed, which means that all the
semantics extracted from \( \tool \) are perfectly correct.
